Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-31 msbr_reproc.tex
rephrasing for clarity

A major problem with the reprocessing method is that different nuclides have 
specific removal rates. On the one hand, if the depletion time intervals are 
very short it means specific isotope being instantly removed, and it is hard to 
obtain equilibrium composition because enormous large number of depletion 
steps. On the other hand, if the depletion calculation time interval is too 
long the results would not truly represent the \gls{MSBR} conceptual design. 
Following this idea, the time interval for depletion calculations was selected 
as 3 days to correlate with the removal interval of $^{233}$Pa. Thorium is 
continuously added to 
maintain the initial mass fraction of $^{232}$ThF$_4$.

>>>>

Since removal rates vary among nuclides in this reactor concept, the Serpent 2 
reprocessing method is unable to capture the desired reprocessing strategy. 
The removal rates also dictate the necessary resolution of depletion 
calculations. If the depletion time intervals are 
very short an enormous number of depletion steps are required to
obtain the equilibrium composition. On the other hand, if the depletion 
calculation time interval is too long, serious impacts of short lived fission 
products are not captured in a manner that is faithful \gls{MSBR} conceptual design. 
To compromise, the time interval for depletion calculations in this model was selected 
as 3 days to correlate with the removal interval of $^{233}$Pa and Thorium was 
continuously added to maintain the initial mass fraction of $^{232}$ThF$_4$.
